---
title: "R Notebook"
output: html_notebook
---

# Accounting for known QTLs in predictions

Using the reference chromosome 4 and chromosome 11 from kayondo et al. for foliar and chromosome 18 from Morag for roots


## Foliar QTLs (chromosome 4 and chromosome 11)

Make relationship matrices for chromosome 4, chromosome 11 and rest of the genome (Just run this once)

```{r}

chr4  <- read.delim("/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/4.dosage", header = TRUE, row.names = 1)
chr11 <- read.delim("/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/11.dosage", header = TRUE, row.names = 1)
rotg  <- read.delim("/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/rest.dosage", header = TRUE, row.names = 1)

chr4.grm    <- A.mat(t(chr4-1))
chr11.grm   <- A.mat(t(chr11-1)) 
rotg.grm    <- A.mat(t(rotg-1))

save(chr4.grm, file = "/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/4.grm")
save(chr11.grm, file = "/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/11.grm")
save(rotg.grm, file = "/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/rotg.grm")

```

### Run the 2 kernel (chromosome 4 & 11) GS Model

```{r}

load("/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/4.grm")
load("/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/11.grm")

#Load the required packages:
library(rrBLUP)
library(foreach)
library(doParallel)

# Load the cross validation code:
source("/home/roberto/Desktop/JL-Presentation/PAG_2017/Code/GBLUP_functions.R")

#Load phenotypic Data (Already Filter no missings or extras)
CBSD_pheno <- read.delim("~/Desktop/JL-Presentation/PAG_2017/Phenotypes/Phenos.txt", stringsAsFactors = F)


# Run the cross-validation

traits<-c("CBSD3S","CBSD6S","CBSDRS")
proctime<-proc.time()
cl<-makeCluster(6)
registerDoParallel(cl)

kernelx2 <- foreach(a=traits, virus=icount(), .inorder=TRUE) %dopar% {
  require(EMMREML)
  crossval<-FoldCrossValidation.V3.emmreml(CBSD_pheno,traits[virus],"CLONE",list(chr11.grm, chr4.grm),5,25)
}

stopCluster(cl)
proc.time() - proctime

save(kernelx2, file = "/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/kernelx2")

```

### Random 2 kernels 
Everything but 4 and 11

Getting relationship matrix for everything (run this only once)
All the relationship markers will be saved in /home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/Dosages/

```{r}

for (i in 1:18) {
  chr <- paste0("chr", i) 
  assign(chr, read.delim(paste0("/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/Dosages/",i,".dosage"), header = TRUE, row.names = 1))
  grms <- paste0(chr, ".grm")
  assign(grms, A.mat(t(get(chr)-1)))
  save(list=grms, file = paste0("/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/Dosages/", grms))
}

```

Run the two kernel model with random chromosome pair in each iteration

```{r}

take <- c(1,2,3,5,6,7,8,9,10,12,13,14,15,16,17,18)

CBSD3 <- matrix(0, nrow=25, ncol = 3)
CBSD6 <- matrix(0, nrow=25, ncol = 3)
CBSDR <- matrix(0, nrow=25, ncol = 3)

colnames(CBSD3) <- c("K1", "K2", "Total")
colnames(CBSD6) <- c("K1", "K2", "Total")
colnames(CBSDR) <- c("K1", "K2", "Total")

for (i in 1:25) {
  
  cromosomas <- sample(take, 2, replace = F)
  k1 <- paste0("chr", cromosomas[1],".grm")
  k2 <- paste0("chr", cromosomas[2],".grm")
  kf <- list(get(k1),get(k2))
  
  traits<-c("CBSD3S","CBSD6S","CBSDRS")

  proctime<-proc.time()
  cl<-makeCluster(6)
  registerDoParallel(cl)
  
  atmp <- foreach(a=traits, virus=icount(), .inorder=TRUE) %dopar% {
  require(EMMREML)
  crossval<-FoldCrossValidation.V3.emmreml(CBSD_pheno,traits[virus],"CLONE",kf ,5,1)
  
  }
  stopCluster(cl)
  proc.time() - proctime
  
  k3 <- atmp[[1]]$accuracies[1,3]
  l3 <- atmp[[1]]$accuracies[1,4]
  m3 <- atmp[[1]]$accuracies[1,5]
  
  k6 <- atmp[[2]]$accuracies[1,3]
  l6 <- atmp[[2]]$accuracies[1,4]
  m6 <- atmp[[2]]$accuracies[1,5]
  
  kr <- atmp[[3]]$accuracies[1,3]
  lr <- atmp[[3]]$accuracies[1,4]
  mr <- atmp[[3]]$accuracies[1,5]
  
  CBSD3[i,] <- c(k3,l3,m3)
  CBSD6[i,] <- c(k6,l6,m6)
  CBSDR[i,] <- c(kr,lr,mr)
  
}

save(CBSD3, file = "/home/roberto/Desktop/JL-Presentation/PAG_2017/Results/Accounting_for_QTL/CBSD3_random.Rdata")
save(CBSD6, file = "/home/roberto/Desktop/JL-Presentation/PAG_2017/Results/Accounting_for_QTL/CBSD6_random.Rdata")
save(CBSDR, file = "/home/roberto/Desktop/JL-Presentation/PAG_2017/Results/Accounting_for_QTL/CBSDR_random.Rdata")

```

Set the dataframes for GGPLOT

```{r}

library(tidyr)
library(magrittr)
library(dplyr)

CBSD3t <- gather(as.data.frame(CBSD3), value = "ACCURACIES", key = "K" ) %>%
  mutate(SET = "Random") %>%
  mutate(TRAIT = "CBSD3")

CBSD6t <- gather(as.data.frame(CBSD6), value = "ACCURACIES", key = "K" ) %>%
  mutate(SET = "Random") %>%
  mutate(TRAIT = "CBSD6")

CBSDrt <- gather(as.data.frame(CBSDR), value = "ACCURACIES", key = "K" ) %>%
  mutate(SET = "Random") %>%
  mutate(TRAIT = "CBSDR")

### Ready to ggplot only Random
Random <- bind_rows(CBSD3t, CBSD6t, CBSDrt)


CBSD3QTL <- kernelx2[[1]]$accuracies %>%
  select(Trait, Acc.K1, Acc.K2, Acc.TotGen ) %>%
  gather(value= "ACCURACIES", key = "K", Acc.K1, Acc.K2, Acc.TotGen)  %>%
  mutate(K = recode(K, "Acc.K1" = "Chr11")) %>%
  mutate(K = recode(K, "Acc.K2" = "Chr4")) %>%
  mutate(K = recode(K, "Acc.TotGen" = "Total")) %>%
  rename(TRAIT = Trait) %>%
  mutate(TRAIT = recode(TRAIT, "CBSD3S" = "CBSD3")) %>%
  mutate(SET = "QTL")

CBSD6QTL <- kernelx2[[2]]$accuracies %>%
  select(Trait, Acc.K1, Acc.K2, Acc.TotGen ) %>%
  gather(value= "ACCURACIES", key = "K", Acc.K1, Acc.K2, Acc.TotGen)  %>%
  mutate(K = recode(K, "Acc.K1" = "Chr11")) %>%
  mutate(K = recode(K, "Acc.K2" = "Chr4")) %>%
  mutate(K = recode(K, "Acc.TotGen" = "Total")) %>%
  rename(TRAIT = Trait) %>%
  mutate(TRAIT = recode(TRAIT, "CBSD6S" = "CBSD6")) %>%
  mutate(SET = "QTL")

CBSDRQTL <- kernelx2[[3]]$accuracies %>%
  select(Trait, Acc.K1, Acc.K2, Acc.TotGen ) %>%
  gather(value= "ACCURACIES", key = "K", Acc.K1, Acc.K2, Acc.TotGen)  %>%
  mutate(K = recode(K, "Acc.K1" = "Chr11")) %>%
  mutate(K = recode(K, "Acc.K2" = "Chr4")) %>%
  mutate(K = recode(K, "Acc.TotGen" = "Total")) %>%
  rename(TRAIT = Trait) %>%
  mutate(TRAIT = recode(TRAIT, "CBSDRS" = "CBSDR")) %>%
  mutate(SET = "QTL")

### Ready to ggplot only QTL
QTL <- bind_rows(CBSD3QTL, CBSD6QTL, CBSDRQTL)

### LOAD I2 INFO > 0.9 GS object

load("/home/roberto/Desktop/JL-Presentation/PAG_2017/Results/Impact_Imputation_level/IMPUTE2.RData")

CBSD3I2 <- IMPUTE2[[1]]$accuracies %>%
  select(Trait, Acc.K1 ) %>%
  gather(value= "ACCURACIES", key = "K", Acc.K1)  %>%
  mutate(K = recode(K, "Acc.K1" = "Total")) %>%
  rename(TRAIT = Trait) %>%
  mutate(TRAIT = recode(TRAIT, "CBSD3S" = "CBSD3")) %>%
  mutate(SET = "WGI")

CBSD6I2 <- IMPUTE2[[2]]$accuracies %>%
  select(Trait, Acc.K1 ) %>%
  gather(value= "ACCURACIES", key = "K", Acc.K1)  %>%
  mutate(K = recode(K, "Acc.K1" = "Total")) %>%
  rename(TRAIT = Trait) %>%
  mutate(TRAIT = recode(TRAIT, "CBSD6S" = "CBSD6")) %>%
  mutate(SET = "WGI")

CBSDRI2 <- IMPUTE2[[3]]$accuracies %>%
  select(Trait, Acc.K1 ) %>%
  gather(value= "ACCURACIES", key = "K", Acc.K1)  %>%
  mutate(K = recode(K, "Acc.K1" = "Total")) %>%
  rename(TRAIT = Trait) %>%
  mutate(TRAIT = recode(TRAIT, "CBSDRS" = "CBSDR")) %>%
  mutate(SET = "WGI")


### Ready to ggplot only QTL
WGI <- bind_rows(CBSD3I2, CBSD6I2, CBSDRI2)

### Merge everything
Accounting <- bind_rows(Random, QTL, WGI)

```

GRAPH

```{r, fig.height=7, fig.width=15}

library(ggplot2)
library(wesanderson)

Accounting$SET <- factor(Accounting$SET, levels=c("QTL", "Random", "WGI"))
Accounting$K <- factor(Accounting$K, levels=c("Chr4", "Chr11", "K1", "K2", "Total"))

kolor <- wes_palette(name = "Zissou")

p <- ggplot(Accounting, aes(factor(K), ACCURACIES))
p + geom_boxplot(aes(fill = SET)) + labs(title="Accounting for known QTLs", x="Imputation level") +  theme_bw() +
  facet_grid(. ~ TRAIT) +
  scale_fill_manual(values = c(kolor[1], "white", kolor[4])) +
  theme(plot.title=element_text(colour = "navyblue",face ="bold", size= 18, margin = margin(t=20, b=20)),
        axis.title.y=element_text(margin=margin(0,20,0,0)),
        axis.text=element_text(size=15), 
        axis.title=element_text(size=20,face="bold"),
        axis.title.x=element_text(margin=margin(20,0,0,0))) 


```


### Kernels x3 (4, 11, EE)
Run the 3 kernel model (chromosome 4, 11 & everything else) GS Model

```{r}

# Run the cross-validation

traits<-c("CBSD3S","CBSD6S","CBSDRS")
proctime<-proc.time()
cl<-makeCluster(6)
registerDoParallel(cl)

load("/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/rotg.grm")

kernelx3 <- foreach(a=traits, virus=icount(), .inorder=TRUE) %dopar% {
  require(EMMREML)
  crossval<-FoldCrossValidation.V3.emmreml(CBSD_pheno,traits[virus],"CLONE",list(chr4.grm, chr11.grm, rotg.grm),5,25)
}

stopCluster(cl)
proc.time() - proctime

save(kernelx3, file = "/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/kernelx3")

```

Get the data frames together

```{r}

# Two kernels
QTL <- bind_rows(CBSD3QTL, CBSD6QTL, CBSDRQTL)

# Three kernels
CBSD33K <- kernelx3[[1]]$accuracies %>%
  select(Trait, Acc.K1, Acc.K2, Acc.K3, Acc.TotGen ) %>%
  gather(value= "ACCURACIES", key = "K", Acc.K1, Acc.K2, Acc.K3, Acc.TotGen)  %>%
  mutate(K = recode(K, "Acc.K1" = "Chr4")) %>%
  mutate(K = recode(K, "Acc.K2" = "Chr11")) %>%
  mutate(K = recode(K, "Acc.K3" = "RG")) %>%
  mutate(K = recode(K, "Acc.TotGen" = "Total")) %>%
  rename(TRAIT = Trait) %>%
  mutate(TRAIT = recode(TRAIT, "CBSD3S" = "CBSD3")) %>%
  mutate(SET = "3K")

CBSD63K <- kernelx3[[2]]$accuracies %>%
  select(Trait, Acc.K1, Acc.K2, Acc.K3, Acc.TotGen ) %>%
  gather(value= "ACCURACIES", key = "K", Acc.K1, Acc.K2, Acc.K3, Acc.TotGen)  %>%
  mutate(K = recode(K, "Acc.K1" = "Chr4")) %>%
  mutate(K = recode(K, "Acc.K2" = "Chr11")) %>%
  mutate(K = recode(K, "Acc.K3" = "RG")) %>%
  mutate(K = recode(K, "Acc.TotGen" = "Total")) %>%
  rename(TRAIT = Trait) %>%
  mutate(TRAIT = recode(TRAIT, "CBSD6S" = "CBSD6")) %>%
  mutate(SET = "3K")

CBSDR3K <- kernelx3[[3]]$accuracies %>%
  select(Trait, Acc.K1, Acc.K2, Acc.K3, Acc.TotGen ) %>%
  gather(value= "ACCURACIES", key = "K", Acc.K1, Acc.K2, Acc.K3, Acc.TotGen)  %>%
  mutate(K = recode(K, "Acc.K1" = "Chr4")) %>%
  mutate(K = recode(K, "Acc.K2" = "Chr11")) %>%
  mutate(K = recode(K, "Acc.K3" = "RG")) %>%
  mutate(K = recode(K, "Acc.TotGen" = "Total")) %>%
  rename(TRAIT = Trait) %>%
  mutate(TRAIT = recode(TRAIT, "CBSDRS" = "CBSDR")) %>%
  mutate(SET = "3K")

K3 <- bind_rows(CBSD33K, CBSD63K, CBSDR3K)

# WGI
WGI <- bind_rows(CBSD3I2, CBSD6I2, CBSDRI2)


# Merge everything

Everything <- bind_rows(QTL, K3, WGI)

```

GRAPH

```{r, fig.height=7, fig.width=15}

library(ggplot2)
library(wesanderson)

Everything$SET <- factor(Everything$SET, levels=c("QTL", "3K", "WGI"))
Everything$K <- factor(Everything$K, levels=c("Chr4", "Chr11", "RG", "Total"))

kolor <- wes_palette(name = "Zissou")

p <- ggplot(Everything, aes(factor(K), ACCURACIES))
p + geom_boxplot(aes(fill = SET)) + labs(title="Is there anything anywhere else?", x="Imputation level") +  theme_bw() +
  facet_grid(. ~ TRAIT) +
  scale_fill_manual(values = c(kolor[5],kolor[1],kolor[3])) +
  theme(plot.title=element_text(colour = "navyblue",face ="bold", size= 18, margin = margin(t=20, b=20)),
        axis.title.y=element_text(margin=margin(0,20,0,0)),
        axis.text=element_text(size=15), 
        axis.title=element_text(size=20,face="bold"),
        axis.title.x=element_text(margin=margin(20,0,0,0))) 



```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
