---
title: "R Notebook"
output: html_notebook
---

# Accounting for known QTLs in predictions

Using the reference chromosome 4 and chromosome 11 from kayondo et al. for foliar and chromosome 18 from Morag for roots


## Foliar QTLs (chromosome 4 and chromosome 11)

Make relationship matrices for chromosome 4, chromosome 11 and rest of the genome (Just run this once)

```{r}

chr4  <- read.delim("/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/4.dosage", header = TRUE, row.names = 1)
chr11 <- read.delim("/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/11.dosage", header = TRUE, row.names = 1)
rotg  <- read.delim("/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/rest.dosage", header = TRUE, row.names = 1)

chr4.grm    <- A.mat(t(chr4-1))
chr11.grm   <- A.mat(t(chr11-1)) 
rotg.grm    <- A.mat(t(rotg-1))

save(chr4.grm, file = "/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/4.grm")
save(chr11.grm, file = "/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/11.grm")
save(rotg.grm, file = "/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/rotg.grm")

```

### Run the 2 kernel (chromosome 4 & 11) GS Model

```{r}

load("/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/4.grm")
load("/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/11.grm")

#Load the required packages:
library(rrBLUP)
library(foreach)
library(doParallel)

# Load the cross validation code:
source("/home/roberto/Desktop/JL-Presentation/PAG_2017/Code/GBLUP_functions.R")

#Load phenotypic Data (Already Filter no missings or extras)
CBSD_pheno <- read.delim("~/Desktop/JL-Presentation/PAG_2017/Phenotypes/Phenos.txt", stringsAsFactors = F)


# Run the cross-validation

traits<-c("CBSD3S","CBSD6S","CBSDRS")
proctime<-proc.time()
cl<-makeCluster(6)
registerDoParallel(cl)

kernelx2 <- foreach(a=traits, virus=icount(), .inorder=TRUE) %dopar% {
  require(EMMREML)
  crossval<-FoldCrossValidation.V3.emmreml(CBSD_pheno,traits[virus],"CLONE",list(chr11.grm, chr4.grm),5,25)
}

stopCluster(cl)
proc.time() - proctime

save(kernelx2, file = "/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/Foliar_QTLS/kernelx2")

```

### Random 3 kernels 
Everything but 4 and 11







Run the 3 kernel model (chromosome 4, 11 & everything else) GS Model

```{r}



```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
