---
title: "R Notebook"
output: html_notebook
---

# PHENOTYPE FILES:

Load Phenotype files
954 individuals with phenotypes. All individuals has phenotypes.

```{r}
#Load phenotypic Data (Already Filter no missings or extras)
CBSD_pheno <- read.delim("~/Desktop/JL-Presentation/PAG_2017/Phenotypes/Phenos.txt", stringsAsFactors = F)
```

# Impact of Imputation level on Prediction Accuracy

## FULL-datasets

Load the Genomic Relationship Matrices for the four datasets
```{r}

#KGBS (GBS)
load(file = "/home/roberto/Desktop/JL-Presentation/PAG_2017/Results/2.Impact_imputation/GBS61K.RData")

#KS1 (BEAGLE Imputed Stage 1)
load(file = "/home/roberto/Desktop/JL-Presentation/PAG_2017/Results/2.Impact_imputation/stage1GRM.Rdata")

#KS2 (BEAGLE Imputed Stage 2)
load(file = "/home/roberto/Desktop/JL-Presentation/PAG_2017/Results/2.Impact_imputation/stage2GRM.RData")

#I2_GRM (IMPUTE2)
load(file = "/home/roberto/Desktop/JL-Presentation/PAG_2017/Genotypes/I2CBSD.grm.Rdata")
I2_GRM <- I2Dosage.grm

```

Running the GBLUP model cross-validation: 5 fold cross-validation (25 reps)

```{r}

#Load the required packages:
library(rrBLUP)
library(foreach)
library(doParallel)

# Load the cross validation code:
source("/home/roberto/Desktop/JL-Presentation/PAG_2017/Code/GBLUP_functions.R")

## GBS ##

traits<-c("CBSD3S","CBSD6S","CBSDRS")
proctime<-proc.time()
cl<-makeCluster(6)
registerDoParallel(cl)

GB_GBS <- foreach(a=traits, virus=icount(), .inorder=TRUE) %dopar% {
  require(EMMREML)
  crossval<-FoldCrossValidation.V3.emmreml(CBSD_pheno,traits[virus],"CLONE",list(KGBS),5,25)
}

stopCluster(cl)
proc.time() - proctime

## BEAGLE stage I ##

traits<-c("CBSD3S", "CBSD6S", "CBSDRS")
proctime<-proc.time()
cl<-makeCluster(6)
registerDoParallel(cl)

BEAGLEI <- foreach(a=traits, virus=icount(), .inorder=TRUE) %dopar% {
  require(EMMREML)
  crossval<-FoldCrossValidation.V3.emmreml(CBSD_pheno,traits[virus],"CLONE",list(KS1),5,25)
}

stopCluster(cl)
proc.time() - proctime


## BEAGLE stage II ##

traits<-c("CBSD3S", "CBSD6S", "CBSDRS")
proctime<-proc.time()
cl<-makeCluster(6)
registerDoParallel(cl)

BEAGLEII <- foreach(a=traits, virus=icount(), .inorder=TRUE) %dopar% {
  require(EMMREML)
  crossval<-FoldCrossValidation.V3.emmreml(CBSD_pheno,traits[virus],"CLONE",list(KS2),5,25)
}

stopCluster(cl)
proc.time() - proctime


## IMPUTE2 ##

traits<-c("CBSD3S", "CBSD6S", "CBSDRS")
proctime<-proc.time()
cl<-makeCluster(6)
registerDoParallel(cl)

IMPUTE2 <- foreach(a=traits, virus=icount(), .inorder=TRUE) %dopar% {
  require(EMMREML)
  crossval<-FoldCrossValidation.V3.emmreml(CBSD_pheno,traits[virus],"CLONE",list(I2_GRM),5,25)
}

stopCluster(cl)
proc.time() - proctime

```

Plot the Accuracies


```{r}

# NEW GBS accuracies
GBSdf <- matrix(0, nrow=75, ncol = 3) 
colnames(GBSdf) <- c("Accuracy", "Set", "Trait")
GBSdf[1:25,1] <- as.numeric(GB_GBS[[1]]$accuracies[,3])
GBSdf[1:25,2] <- "GBS"
GBSdf[1:25,3] <- "CBSD3MAP"
GBSdf[26:50,1] <- as.numeric(GB_GBS[[2]]$accuracies[,3])
GBSdf[26:50,2] <- "GBS"
GBSdf[26:50,3] <- "CBSD6MAP"
GBSdf[51:75,1] <- as.numeric(GB_GBS[[3]]$accuracies[,3])
GBSdf[51:75,2] <- "GBS"
GBSdf[51:75,3] <- "CBSDR"

# OLD GBS vector from ~/Desktop/JL-Presentation/Accuracies##
vector <- c(0.39,0.42,0.40,0.39,0.40,0.40,0.38,0.40,0.39,0.38,0.367,0.4,0.409,0.398,0.3849,0.3865, 0.3924, 0.3973, 0.3847, 0.4132, 0.3728, 0.3818, 0.4088, 0.39,0.3831)
GBSdf[,1] <- as.numeric(vector)
GBSdf[,2] <- "GBS"
GBSdf[,3] <- "NN"

# BEAGLE STAGE I accuracies
Stage1 <- matrix(0, nrow=75, ncol = 3) 
colnames(Stage1) <- c("Accuracy", "Set", "Trait")
Stage1[1:25,1] <- as.numeric(BEAGLEI[[1]]$accuracies[,3])
Stage1[1:25,2] <- "BEAGLE-1"
Stage1[1:25,3] <- "CBSD3MAP"
Stage1[26:50,1] <- as.numeric(BEAGLEI[[2]]$accuracies[,3])
Stage1[26:50,2] <- "BEAGLE-1"
Stage1[26:50,3] <- "CBSD6MAP"
Stage1[51:75,1] <- as.numeric(BEAGLEI[[3]]$accuracies[,3])
Stage1[51:75,2] <- "BEAGLE-1"
Stage1[51:75,3] <- "CBSDR"

# BEAGLE STAGE II accuracies
Stage2 <- matrix(0, nrow=75, ncol = 3) 
colnames(Stage2) <- c("Accuracy", "Set", "Trait")
Stage2[1:25,1] <- as.numeric(BEAGLEII[[1]]$accuracies[,3])
Stage2[1:25,2] <- "BEAGLE-2"
Stage2[1:25,3] <- "CBSD3MAP"
Stage2[26:50,1] <- as.numeric(BEAGLEII[[2]]$accuracies[,3])
Stage2[26:50,2] <- "BEAGLE-2"
Stage2[26:50,3] <- "CBSD6MAP"
Stage2[51:75,1] <- as.numeric(BEAGLEII[[3]]$accuracies[,3])
Stage2[51:75,2] <- "BEAGLE-2"
Stage2[51:75,3] <- "CBSDR"

# IMPUTE2 accuracies
Impute2 <- matrix(0, nrow=75, ncol = 3) 
colnames(Impute2) <- c("Accuracy", "Set", "Trait")
Impute2[1:25,1] <- as.numeric(IMPUTE2[[1]]$accuracies[,3])
Impute2[1:25,2] <- "IMPUTE2"
Impute2[1:25,3] <- "CBSD3MAP"
Impute2[26:50,1] <- as.numeric(IMPUTE2[[2]]$accuracies[,3])
Impute2[26:50,2] <- "IMPUTE2"
Impute2[26:50,3] <- "CBSD6MAP"
Impute2[51:75,1] <- as.numeric(IMPUTE2[[3]]$accuracies[,3])
Impute2[51:75,2] <- "IMPUTE2"
Impute2[51:75,3] <- "CBSDR"

graph <- rbind(GBSdf, Stage1, Stage2, Impute2)
acc <- as.numeric(graph[,1])

graph <- as.data.frame(graph)
graph[,1] <- acc

```

Loading required packages and plotting

```{r}

library(ggplot2)
require(reshape2)
library(wesanderson)

graph$Set <- factor(graph$Set, levels=c("GBS", "BEAGLE-1", "BEAGLE-2", "IMPUTE2"))

p <- ggplot(graph, aes(factor(Trait), Accuracy))
p + geom_boxplot(aes(fill = Set)) + labs(title="Impact of Imputation Level on Accuracy", x="Imputation level") +  theme_bw() +
  scale_fill_manual(values = wes_palette("Zissou")) +
  theme(plot.title=element_text(colour = "navyblue",face ="bold", size= 18, margin = margin(t=20, b=20)),
        axis.title.y=element_text(margin=margin(0,20,0,0)),
        axis.text=element_text(size=15), 
        axis.title=element_text(size=20,face="bold"),
        axis.title.x=element_text(margin=margin(20,0,0,0))) 



```


## IMPUTE2 AR/subset
What happens when we use only the GBS markers but imputed using Impute2

```{r}

I2GBS.dosage <- read.delim("/home/DB2/Imputation/IMPUTE2/PROCCESING/WORKING/IMPUTE2_at_gbs.dosage", header = TRUE, row.names = 1)
I2GBS.grm <- A.mat(t(I2GBS.dosage-1)) 


traits<-c("CBSD3S", "CBSD6S", "CBSDRS")
proctime<-proc.time()
cl<-makeCluster(6)
registerDoParallel(cl)

IMPUTE2GBS <- foreach(a=traits, virus=icount(), .inorder=TRUE) %dopar% {
  require(EMMREML)
  crossval<-FoldCrossValidation.V3.emmreml(CBSD_pheno,traits[virus],"CLONE",list(I2GBS.grm),5,25)
}

stopCluster(cl)
proc.time() - proctime


```

What happens when we use only the higly accurate imputed markers AR2 > 0.9

```{r}

I290.dosage <- read.delim("/home/DB2/Imputation/IMPUTE2/PROCCESING/FILTERS/CBSD.I2_0.9.dosage", header = TRUE, row.names = 1)
I290.grm <- A.mat(t(I2GBS.dosage-1)) 


traits<-c("CBSD3S", "CBSD6S", "CBSDRS")
proctime<-proc.time()
cl<-makeCluster(6)
registerDoParallel(cl)

IMPUTE290 <- foreach(a=traits, virus=icount(), .inorder=TRUE) %dopar% {
  require(EMMREML)
  crossval<-FoldCrossValidation.V3.emmreml(CBSD_pheno,traits[virus],"CLONE",list(I290.grm),5,25)
}

stopCluster(cl)
proc.time() - proctime


```

```{r}

# NEW GBS accuracies
GBSdf <- matrix(0, nrow=75, ncol = 3) 
colnames(GBSdf) <- c("Accuracy", "Set", "Trait")
GBSdf[1:25,1] <- as.numeric(GB_GBS[[1]]$accuracies[,3])
GBSdf[1:25,2] <- "GBS"
GBSdf[1:25,3] <- "CBSD3MAP"
GBSdf[26:50,1] <- as.numeric(GB_GBS[[2]]$accuracies[,3])
GBSdf[26:50,2] <- "GBS"
GBSdf[26:50,3] <- "CBSD6MAP"
GBSdf[51:75,1] <- as.numeric(GB_GBS[[3]]$accuracies[,3])
GBSdf[51:75,2] <- "GBS"
GBSdf[51:75,3] <- "CBSDR"

# IMPUTE2 accuracies
Impute2 <- matrix(0, nrow=75, ncol = 3) 
colnames(Impute2) <- c("Accuracy", "Set", "Trait")
Impute2[1:25,1] <- as.numeric(IMPUTE2[[1]]$accuracies[,3])
Impute2[1:25,2] <- "IMPUTE2"
Impute2[1:25,3] <- "CBSD3MAP"
Impute2[26:50,1] <- as.numeric(IMPUTE2[[2]]$accuracies[,3])
Impute2[26:50,2] <- "IMPUTE2"
Impute2[26:50,3] <- "CBSD6MAP"
Impute2[51:75,1] <- as.numeric(IMPUTE2[[3]]$accuracies[,3])
Impute2[51:75,2] <- "IMPUTE2"
Impute2[51:75,3] <- "CBSDR"

# IMPUTE2GBS accuracies (only GBS sites)
Impute2GBS <- matrix(0, nrow=75, ncol = 3) 
colnames(Impute2GBS) <- c("Accuracy", "Set", "Trait")
Impute2GBS[1:25,1] <- as.numeric(IMPUTE2GBS[[1]]$accuracies[,3])
Impute2GBS[1:25,2] <- "Impute2GBS"
Impute2GBS[1:25,3] <- "CBSD3MAP"
Impute2GBS[26:50,1] <- as.numeric(IMPUTE2GBS[[2]]$accuracies[,3])
Impute2GBS[26:50,2] <- "Impute2GBS"
Impute2GBS[26:50,3] <- "CBSD6MAP"
Impute2GBS[51:75,1] <- as.numeric(IMPUTE2GBS[[3]]$accuracies[,3])
Impute2GBS[51:75,2] <- "Impute2GBS"
Impute2GBS[51:75,3] <- "CBSDR"

# IMPUTE290 accuracies (only GBS sites)
Impute290 <- matrix(0, nrow=75, ncol = 3) 
colnames(Impute290) <- c("Accuracy", "Set", "Trait")
Impute290[1:25,1] <- as.numeric(IMPUTE290[[1]]$accuracies[,3])
Impute290[1:25,2] <- "Impute290"
Impute290[1:25,3] <- "CBSD3MAP"
Impute290[26:50,1] <- as.numeric(IMPUTE290[[2]]$accuracies[,3])
Impute290[26:50,2] <- "Impute290"
Impute290[26:50,3] <- "CBSD6MAP"
Impute290[51:75,1] <- as.numeric(IMPUTE290[[3]]$accuracies[,3])
Impute290[51:75,2] <- "Impute290"
Impute290[51:75,3] <- "CBSDR"


graph2 <- rbind(GBSdf, Impute2, Impute2GBS, Impute290)
acc <- as.numeric(graph2[,1])

graph2 <- as.data.frame(graph2)
graph2[,1] <- acc
```

Graph

```{r}

graph2$Set <- factor(graph2$Set, levels=c("GBS", "IMPUTE2", "Impute2GBS", "Impute290"))

p <- ggplot(graph2, aes(factor(Trait), Accuracy))
p + geom_boxplot(aes(fill = Set)) + labs(title="Impact of Imputation Level on Accuracy", x="Imputation level") +  theme_bw() +
  scale_fill_manual(values = wes_palette("Zissou")) +
  theme(plot.title=element_text(colour = "navyblue",face ="bold", size= 18, margin = margin(t=20, b=20)),
        axis.title.y=element_text(margin=margin(0,20,0,0)),
        axis.text=element_text(size=15), 
        axis.title=element_text(size=20,face="bold"),
        axis.title.x=element_text(margin=margin(20,0,0,0))) 


```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
