---
title: "Principal Component Regressions on the phenotypes"
output: html_notebook
---

# Check if the phenotypes are explained by the first 10 PCAs

## Calculate the PCs using SNP relate

```{r}

library(gdsfmt)
library(SNPRelate)

bed.fn <- "/home/roberto/Desktop/JL-Presentation/PAG_2017/Genotypes/PLINK/plink.bed"
fam.fn <- "/home/roberto/Desktop/JL-Presentation/PAG_2017/Genotypes/PLINK/plink.fam"
bim.fn <- "/home/roberto/Desktop/JL-Presentation/PAG_2017/Genotypes/PLINK/plink.bim"

snpgdsBED2GDS(bed.fn, fam.fn, bim.fn,out.gdsfn ="test1.gds")
snpgdsSummary("test1.gds")

genofile <- snpgdsOpen("test1.gds")

pca <- snpgdsPCA(genofile, num.thread=2)

PCs <- pca$eigenvect[,1:10]

```

## Get the phenotypes 

```{r}

#Load phenotypic Data (Already Filter no missings or extras)
CBSD_pheno <- read.delim("~/Desktop/JL-Presentation/PAG_2017/Phenotypes/Phenos.txt", stringsAsFactors = F)

newnames <- vector()
for (i in 1:length(pca$sample.id)) {
      newnames <- c(newnames, strsplit(pca$sample.id, ":")[[i]][1])
}

PCs                  <- cbind(PCs,newnames)         
rownames(CBSD_pheno) <- CBSD_pheno[,1] 
PC           <- as_data_frame(PCs)

#PC           <- PC[,-c(12,13,14)]

keep         <- (which(newnames%in%rownames(CBSD_pheno)))
PC           <- PC[keep,]
colnames(PC) <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten", "CLONE")
pnames <- PC$CLONE
PC           <- PC[-which(duplicated(pnames)),]

rownames(PC) <- PC$CLONE

PCpheno <- inner_join(CBSD_pheno, PC)

test <- lm(as.numeric(PCpheno$CBSD6S) ~ as.numeric(PCpheno$six))
cd <- summary(test)
cc <- anova(test)
cc$`Pr(>F)`[1]

```

## Loop and output nicely

```{r}

principals <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten") 


pvalues <- vector()
variance <- vector()

for ( i in 1:10) {
  
  thispc <- i + 10
  test <- lm(as.numeric(PCpheno$CBSDRS.ebv) ~ as.numeric(PCpheno[,thispc]))
  sum <- summary(test)
  ano <- anova(test)
  
  r2   <- sum$adj.r.squared 
  pval <- ano$`Pr(>F)`[1]
  
  pvalues <- c(pvalues, pval)
  variance <- c(variance, r2)
  
}

pval3
variance3 

pval6 
variance6 

pvalr 
variancer


```

## Put everything on dataframes 

```{r}

pvalmatrix <- matrix(0, nrow = 30, ncol = 3)
pvalmatrix <- as.data.frame(pvalmatrix)

colnames(pvalmatrix) <- c("pval", "PC", "Trait")
pvalmatrix[,1] <- c(pval3, -log(pval6), -log(pvalr))
pvalmatrix[,2] <- rep(1:10, 3)
pvalmatrix[,3] <- c(rep("CBSD3",10), rep("CBSD6",10), rep("CBSDR",10))


varamatrix <- matrix(0, nrow = 30, ncol = 3)
varamatrix <- as.data.frame(varamatrix)

colnames(varamatrix) <- c("r2", "PC", "Trait")
varamatrix[,1] <- c(variance3, variance6, variancer)
varamatrix[,2] <- rep(1:10, 3)
varamatrix[,3] <- c(rep("CBSD3",10), rep("CBSD6",10), rep("CBSDR",10))

-log(pval6)
```


## Plot

```{r}


library(ggplot2)
library(wesanderson)

#Everything$SET <- factor(Everything$SET, levels=c("QTL", "3K", "WGI"))
#Everything$K <- factor(Everything$K, levels=c("Chr4", "Chr11", "RG", "Total"))


p <- ggplot(data=pvalmatrix, aes(x=as.character(PC), y=pval, group=Trait, colour=Trait)) 
p + geom_line() +
    geom_point()

g <- ggplot(data=varamatrix, aes(x=as.character(PC), y=r2, group=Trait, colour=Trait)) 
g + geom_line() +
    geom_point()






```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
